### 2016-01-16 paper.tex
Built --> fabricated per @wosnik
Prescription --> precise control per @wosnik

A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
parameters were scaled from the RM2 design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
model \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

@@

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed prescription of
the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer. A load cell mounted, mounted at a fixed distance from the
servo motor, provides a redundant measurement. Turbine shaft angle was measured
using the servo drive's emulated encoder output, set to $10^5$ counts per
turbine shaft revolution. Carriage speed, and therefore inflow velocity was
measured using a linear encoder with 10 $\mu$m resolution. All of these
performance-related quantities were sampled at 2 kHz, while the tow tank's
motion controller provided redundant measurements of the carriage speed turbine
angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

>>>>

A 1:6 scale model of the RM2 rotor was designed and fabricated. Turbine
geometric parameters were scaled from the RM2 design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
model \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

@@

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed precise control
of the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer. A load cell mounted, mounted at a fixed distance from the
servo motor, provides a redundant measurement. Turbine shaft angle was measured
using the servo drive's emulated encoder output, set to $10^5$ counts per
turbine shaft revolution. Carriage speed, and therefore inflow velocity was
measured using a linear encoder with 10 $\mu$m resolution. All of these
performance-related quantities were sampled at 2 kHz, while the tow tank's
motion controller provided redundant measurements of the carriage speed turbine
angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
